Check Coverage

### 2019-10-25 analysis/merge_data.Rmd
Get FD for all data

data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(study_id == 516)

@@

plan(multiprocess)
fd <- future_map_dfr(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2]))  
```

>>>>

data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(!study_id %in% c(195, 360), #exclude because they break
         !study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

plan(multiprocess)
system.time(fd <- future_map_dfr(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2])))
```
